\documentclass[11pt]{pnas-new}
% \documentclass[10pt]{article}
\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{xcolor,ulem}
\usepackage{mdframed}
\usepackage{wrapfig}
\usepackage{multicol}
\setlength{\columnsep}{1cm}
\usepackage{graphicx}
\usepackage{adjustbox}
\usepackage{lipsum}
\newlength{\strutheight}
%\usepackage{soul} % for strike-through (\st)

\author[1]{Hau-Tieng Wu}
\author[2]{Yoav Freund}

\affil[1]{Duke, Mathematics and Statistical Science, Durham, 27708, USA}
\affil[2]{UCSD, Computer Science, San Diego, 92093, United States. yfreund@eng.ucsd.edu}


\title{Trusted digital doctors know their limits}

\input{macros}
\renewcommand{\input}[1]{}

\begin{abstract}

  The meteoric rise of AI in general and Deep Learning in particular
  is generating great excitement throughout academia and commerce, and
  in particular in medicine\cite{topol2019deep,
    wachter2015digital}. With some some high-profile claims
  that AI will soon replace humans in many medical specialties.

  In this position paper we present an alternative view. We contrast
  {\em Artificial Intelligence} with {\em Intelligence Augmentation}
  and argue that the second is more likely to benefit the patient than
  the first. We provide evidence to this argument and present a vision
  in which easier decisions are delegated to computers, while the more
  difficult ones are handled by humans.

\end{abstract}

\begin{document}
\settoheight{\strutheight}{\strut}

 
\maketitle

%\thispagestyle{firststyle}
\iffalse
\section{issues to be resolved}

\hautieng{As we discussed, I followed the medical journal convention and changed the author order so that you are the senior/corresponding author.}

\begin{itemize}
    \item Introduce the term "Healthcare Provider" with acronym HP, and use throughout instead of doctors nurses etc. \hautieng{I am not sure what is the best way to do it. In many places, "doctor" are clearly more precise than HP. So I leave this part to you.}
    \item Patient compliance - how can IA help make sure that patients take their meds, don’t drink excessively etc. \hautieng{done}
    \item Compensation: Doctors that generate quality data should own this data, distribution mechanisms should compensate the doctor for his/her contribution. \hautieng{As we discussed, this might be a bit off the topic. This is more like a regulatory issue. Let's discuss it if you have a different viewpoint.}
    \item A few grammatical corrections:
    -insert 2 page 2 last line “piopsies” instead of biopsies
    -last line page 2 spelling: “therefor” (needs an e) therefore 
    -insert page 7 we quote from Robert Rechter’s book... (53) Reference @ 53 indicates “Robert Wachter” as author. \hautieng{I am not fully sure what you want...}

\end{itemize}

To Highlight a change use this macro: \change{old text}{new text}
\fi

\section{Introduction}

The meteoric rise of AI and Deep learning raises the possibility that
doctors will be replaced by computers~\cite{Mukherjee2017}. Geoff Hinton,
a famous deep learning researcher said in 2017: ``It's just completely
obvious that in ten years deep learning is going to do better than
Radiologists ... They should stop training radiologists now''.

The predictions of Sebastian
Thrun~\cite{Mukherjee2017,esteva2017dermatologist}, another leader in
machine learning, are less disruptive: ``... deep learning devices
will not replace dermatologists and radiologists. They will {\em
  augment} professionals, offering the expertise and assistance''. 
  The term "Augmented Intelligence" appears frequently in recent 
  policy reports from medical associations~\cite{american2019augmented,AAD2019augmented}. Collaborations between computers and human care-givers are seen as a desirable goal.
  In this article we suggest how such a collaboration between human and computer might unfold in practice. Central to our approach is to allow the computer to quantify it's own uncertainty and, when appropriate, output "I don't know" (which we will abbreviate as IDK).
 
\input{AIIABox} The argument as to whether human healthcare providers (HP~\footnote{Our discussion applies to all healthcare providers, including Doctors, Nurse Practitioners and Nurses. To simplify the references o this group of professionals we use the acronym HP, which stands for "Healthcare Provider"}  will be replaced or empowered by computers is a recent
incarnation of a long standing debate between AI (Artificial Intelligence) and IA
(Intelligence amplification) (see inset).

To distinguish between the goals of AI and IA we use the 
terms ``AI agent'' and ``IA
sidekick''. This terminology contrasts {\em agents}, which are endowed
with {\em agency} and can take {\em actions} that effect the patient's
health, with {\em sidekicks}, which can provide advice and suggestions,
but who are not allowed to take an action.

Of the many potential uses of AI/IA in medicine, we focus on diagnostics.
AI-driven diagnosis are expected to become a reality much sooner than other medical activities such as surgery~\cite{topol2019deep}. 

Central to our argument is a quantification of {\em prediction
  confidence}. Such quantification is needed to avoid premature
diagnostic conclusions, and to decide which additional tests or
consultations might be needed. Consider a doctor that is asked
to diagnose a patient with complex or conflicting symptoms. A careful
doctor will admit their uncertainty and perform additional tests or
ask a specialist. A less careful, overly self confident doctor is
likely give an incorrect diagnosis and choose an ineffective or even damaging
treatment plan.

An AI agent, expected to be better than the human HP, is more likely to 
end up behaving like an overly confident doctor. An IA sidekick, aware of
it's own limitations, will give advice only when the evidence is
strong and otherwise say ``I don't know''.

In the following sections we explore these ideas in more detail. We
start with a critique of one of the papers that claims that AI agents
can outperform human diagnosticians.

\section{Supervised Learning and the Ground Truth}
\label{sec:ground-truth}

Deep learning (DNN) is a special case of {\em supervised learning} (see
inset), sometimes called {\em input-output}
learning~\cite{ng2016artificial,topol2019deep}.

Examples of applications of DNN to medical diagnosis include arrhythmia classification 
from single channel electrocardiogram \cite{hannun2019cardiologist}, diabetic retinopathy detection from retinal fundus photographs \cite{gulshan2016development}, skin cancer diagnostics~\cite{esteva2017dermatologist} as well as many others.

\input{Supervised}
The data for supervised learning consists of a large collection of
(input, output) pairs. For medical diagnosis, usually the input is medical
information for the patient (Heart rate, blood tests, X-ray images
etc.) and the output is the diagnosis. This output is considered the
``ground-truth'' and is assumed to represent the undisputed truth.

Here lies the first difficulty with applying supervised learning
to medical diagnosis. In this context the labels correspond to 
the judgement of human diagnosticians. However 
different diagnosticians might give different diagnoses, in which case it is hard to assign ground truth. 
We will return to this important issue in the next section.

The other important assumption made in supervised learning is that the
generated classifier is tested using the same distribution of examples
as that of the training set.

\input{SkinCancer}
A highly cited paper in the journal Science~\cite{esteva2017dermatologist}
makes the claim that DNNs can perform diagnostics as well as, or better, than board certified dermatologists. (see inset)

A fundamental problem with the experiments presented in the paper is 
the way the data was
collected. The data used in the experiment was {\em retrospective},
i.e., it was collected from the records of past patients for which both
a skin image and a biopsy were available. Normally, patients get
biopsied only if the dermatologist thinks there is a significant
chance of {\bf malignancy}. As a result, a retrospective study that is
based on patients for whom a biopsy was taken is likely to
over-represent malignant patients and therefore be biased. If an image-based classifier
is trained on the biased data, its performance on unbiased test data
is likely to be worse. Specifically, when the classifier is applied to skin
images of un-diagnosed patients it is likely to over-diagnose them as
malignant. The practical implication would be that more patients than
necessary will be biopsied. 

As we elaborate on in the next section, in medical diagnostics the
{\em ground truth} are often unavailable, all that we have to go on are
the opinions of human diagnosticians.

\section{Uncertainty in medicine}

\input{Arrhythmia}
One of the methods of quantifying uncertainty in medical diagnosis is inter-rater studies.
In studies of this kind, multiple doctors produce diagnostics
based on identical medical information without communicating with each other. (see inset).
Associating {\em ground Truth} with these diagnostics whose inter-rater agreement is less than perfect is challenging.
 
In addition, diagnosis is not an
input-output mapping. Rather, it is an iterative process which reduces
uncertainty over time. To illustrate this, consider the diagnostics of
a patient that is treated in an out-patient clinic.  When a patient
arrives at a clinic for the first time, all diagnostics are
possible. After a physical exam and an interview with a doctor, many
possibilities are eliminated.
\input{InterRaterAgreement}

In {\em simple} cases, this is enough
for the doctor to confidently choose a treatment. In more complex
cases, the doctor might ask for multiple tests and visits, refer the
patient to a specialist, consult colleagues, journals and books,
etc. To choose a treatment plan, the set of possible diagnostics has
to be reduced.  However, it does not have to be reduced to a {\em
  single} diagnosis before treatment can be started.

In order to apply a supervised learning method, such as  DNN, to the
diagnostics problem, one needs to define a {\em ground-truth} diagnostic for each
patient. However, that is easier said than done. Currently, most of
the data available for machine learning is {\em observational or
retrospective data}; that is, data has been collected
during the diagnosis and treatment of patients.
One way to confirm a diagnosis is to collect more information through
additional examinations and tests. However the attending medic might
judge additional tests to be unnecessary, in which case the outcome of these tests will not
appear in the observational study.
Another way is following up on the treatment plan. However, correct
diagnosis is only one of many factors that influence the long term
health of the patient. Others include choice of treatment, medication
adherence, change in diet or reduction in stress, among many others.

\input{SignalQuality}
There are many causes for uncertainty in medical diagnosis. We briefly
describe three categories of problems: {\em signal quality}, the {\em
  knowledge gap} and the limitations of {\em diagnostic protocols}.

By {\em Signal Quality} we refer to the quality of the raw data
collected for medical diagnosis. Some diagnostic measures, such
as heart rate, blood pressure and temperature can be measured more reliably
and consistently than other
measures such as EKG, EEG, camera images, X-ray, ultrasound and MRI, some of which might
produce vast and highly variable data. The quality of this data
depends on many factors among them, including the quality of the instruments, the
consistency of the human operator, the build of the patient, etc.

\input{AlarmFatigue}
Signal quality enhancement is already an important part of imaging
devices such as X-ray and MRI. Methods such as compressed
sensing~\cite{lustig2008compressed} are used to reconstruct 3d images
from a large number of noisy scans.

One situation where signal quality and signal variability cannot be
neglected is Patient Monitors.  The purpose of these devices is to
continuously monitor patients vital signs and alert the medical staff
if a dangerous situation is detected. Unfortunately, the false alarm
rate of these devices is often high. This results in a phenomenon
called ``alarm fatigue'' (see inset) where the medical staff ignores
the generated alarms, rendering them less clinically useful than
expected.

Signal quality and alarm fatigue can be thought of as ``bottom up''
causes of uncertainty. The uncertainty originates in the medical
devices and moves up to the HP.

Other types of uncertainty are ``top down'' in that they originate in medical research percolates down to the HP. We briefly
describe two types of top-down uncertainty: knowledge gaps and the
limitation of medical protocols.

{\em ``Knowledge gap''} corresponds to limitations of scientific medical
knowledge. This is not the limitation of a particular doctor; rather,
it reflects the limitations of knowledge that correspond to successful
medical trials.
\input{KnowledgeGap}

Even when medical knowledge exists, an individual doctor might not
possess it. The dissemination of up to date and reliable medical
information is far from even. One of the important information
dissemination tools are {\em medical protocols}. Those are used to
ensure uniformity and consistency of treatment between hospitals,
doctors and nurses. While protocols are an important dissemination
tool, they have some limitations, as described in the inset.
~\\

\section{Uncertainty in machine learning}

We described some of the many causes of uncertainty in medical
diagnosis. One might conclude that the automation of diagnosis in
diseases with high rates of inter-rater disagreement is
impossible. However, this is not necessarily the case. There are types
of diagnostics for which the typical case is {\em simple}, and only a
small fraction of the cases are {\em complex}.  We use the term
``simple'' to mean that {\em most doctors are likely to give the same
  diagnosis}.  In other words, these are the cases on which
inter-rater {\em dis}agreement is low. ``Complex'' cases are those where
doctors tend to either say "I don't know" or disagree with each other.
{\em Our proposal is to allow IA to output IDK on
  the complex cases, and, in exchange, require higher levels of
  accuracy and reliability when the IA makes a prediction.}

Increasing confidence in a diagnosis by seeking consensus among
several doctors is common sense. A similar approach has been used in
machine learning algorithms such as Bagging~\cite{breiman1996bagging},
Random Forests~\cite{breiman2001random}, and
Boosting\cite{SchapireFr2012}. These so-called ``ensemble'' algorithms
take the majority vote of predictions from several ``base'' learning
algorithms using a majority vote to generate a single more reliable
prediction.~\footnote{A majority is used when there are only two
  possible labels. A more general combination rule is the {\em
    plurality} i.e., the label that gets the largest number of votes.}

The majority vote always outputs one of the labels. A {\em dominant
  majority rule} for binary prediction is one that outputs +1 or -1,
if one of the classes gets {\em significantly} more votes than any of
the others. If the number of votes for both labels are similar, the
dominant majority rule outputs ``?'' which is interpreted as ``I don't
know''.

\section{Augmenting medicine}

\input{ProtocolLimitations}
The goal of this paper is to chart a path by which machine learning
and big data can be effectively used in medicine. Our discussion
focuses on the differences between AI and IA and we argue that IA
defines more achievable goals.

We use Ronald Heifetz classification of problems (see inset). Our
discussion up to this point focused on {\em technical}
problems. Technical issues can be solved by changing equipment or
directions for its use. In the remainder of this article we will
concern ourselves with the much harder {\em adaptive}
problems. Adaptive problems require changes in the perception and
behavior of {\em people}. In our case people are the caregivers who
are supposed to use the new technology. The best technology is
worthless if it is not adopted.

Consider first an AI system developed with the goal of replacing the
caregiver. Naturally, the caregiver will prefer not to use the
system. Will the patient prefer the human caregiver or the AI system?
The answer is anybody's guess, because such systems are not available
yet. Studies show that patients trust a human caregiver more than
technology \cite{ongena2020patients}, and that trust requires a human
to human connection \cite{nundy2019promoting}.

Unlike AI, IA systems do not aim to replace the caregiver. Rather,
they aim to assist the caregiver by taking care of the simple or easy
cases, and deferring to the human for the more complex cases. In this way IA can 
achieve the goal of ``computer and human work together'' \cite{verghese2018computer}. 
This makes the caregiver more efficient and effective, but does
not take away the agency and humanity of the caregiver. When the IA system outputs
``I don't know'' it explicitly passes the responsibility for the
patient to the caregiver.

%Agency and responsibility are central to patient-caregiver
%relationship.

As discussed earlier, medical cases often fall within gray areas, where
medics differ on the correct diagnosis or the best treatment. In such
cases the caregiver has the responsibility of making a decision even
though the decision might be wrong. Price et. al. have studied the ethical,
legal and regulatory aspects of using AI in
medicine.\cite{price2014black,ford2016privacy, price2017regulating}
Their conclusion is that the ultimate responsibility for the patients
well-being is {\em always} with the human caregiver. Even if the AI
system is known to make fewer mistakes than the average doctor,
mistakes are unavoidable, and the question is who is held responsible for
the mistake, and who needs to explain their decisions and potentially lose their license to practice.

\iffalse

In this book the point is made that human error is inevitable.
\yoav{ What is the main point of this paper? \cite{donaldson2000err}}

\sout{
Today, and in the foreseeable
future, \sout {\color{blue}non-trivial efforts are needed to convert} medicine \sout{will not be}{\color{blue}to} a precise science. {\color{blue}Even if medicine fulfills precise science,} incorrect decisions {\color{blue}is inevitable due to human natures \cite{donaldson2000err}, and }
can result in harm or death.  }
\fi

We give three perspectives on the possible integration of IA with
medicine: IA and the individual medic, the decentralization of
medicine, and IA as a method for disseminating medical knowledge.

\subsection{IA and the individual medic}

\input{TechnicalVSAdaptive} 
From the perspective of an individual medic, an IA sidekick is a
tool that augments their diagnostic abilities by increasing accuracy
and by saving time.

To better understand the diagnostic process and the possibilities  of
improving it using IA, we turn to the Kahaneman's~\cite{kahneman2011thinking}
``Thinking Fast Thinking Slow'' and to Vordermark book on medical
decision making~\cite{vordermark2019introduction}. According to these authorities,
medical diagnosis is a combination of two types of processes: {\em
  recognition} and {\em elimination}.

{\em Recognition} is an automatic mental process where one diagnosis
presents itself in the doctors mind as truth. Pathologists,
Radiologist's and other ``Pattern Doctors''~\cite{topol2019deep} make heavy use
of recognition. Their experience allows them to quickly sift through
large amounts of data and detect complex patterns. Pattern Doctors
often work under great time pressure, which can cause them to miss
important patterns. IA can help the doctor by performing a fast
analysis of the signal and alerting the doctor to locations that might
indicate a pathology. This improves the accuracy and speed of the
pathologist while maintaining the responsibility of the doctor to the
final diagnostics. 

Pattern doctors are often unable to fully explain their diagnostics.
This hinders documenting, critiquing and teaching diagnostics. As
recognition typically points to a single diagnosis, there is a danger
of overlooking other possible diagnoses. IA can serve as a ``note
taker'' documenting the diagnostic process, and pointing out possible
errors of omission. 

An example of a pattern classification problem is the annotation of
sleep. There is active research on using AI to automate this task
\cite{sleepHT2020}.
There is significant inter-rater agreement rate among experts for 
{\em normal subjects}, it is still far from perfect. Agreement drops significantly for abnormal subjects with subjects with sleep apnea   ... . 
Existing systems, however, output the identified sleep stages, 
without providing any measure of confidence. Providing a measure of confidence allows the HP to concentrate on the complex parts of the signal, while delegating the easy pars to IA sidekick. We believe that such division of labor will increase the likelihood that the HP would use the IA system.

An ideal IA
sidekick should let experts know "I don't know", where there is any
ambiguity in the process of annotation. Suppose there are 10\% "I
don't know" sleep stages, it could help save experts 90\% of time, and
focus on more important issues.

{\em Elimination}, unlike recognition, is a slow deliberative and
verbal process which starts with all possible diagnoses and gradually
eliminates unlikely ones based on patient history, examination and
test results. As Elimination is deliberative, it is easier to discuss,
document and teach it.

An IA system could help the elimination process carefully and
systematically eliminate diagnoses. This can help the doctor stay
aware of possibilities that are not obvious, for differential
diagnosis.


\subsection{IA and Decentralized medicine}

Medicine today is highly centralized. Most interactions
between patient and medic occur in hospitals and clinics. These
large facilities are expensive to build and to maintain. Traveling to
a hospital and back in order to see a doctor for 5 minutes is highly
inefficient. 

Part of the solution is telemedicine. In these days of Covid-19,
telemedicine has gained popularity. Medic and patient can meet in a
virtual space without either leaving home. Moreover, diagnostic
devices can be placed in the patient's home and provide the doctor with
vital signs.


Devices exist that allow most patients to measure basic vital signs
such as blood pressure, heart rate, EKG and temperature. More complex signals such as
polysomnogram or ultrasound currently require a local nurse or a
technician and/or a local facility outside the home.

IA can reduce the need for a nurse or technician in two ways. First,
it can guide the patients in placing the sensors on his/her
body so as to get a good signal or image. Second, it can perform an
initial diagnosis. If the patterns are simple, output a diagnosis.
Otherwise, output IDK and alert the remote healthcare provider. 

One significant disadvantage of decentralized medicine is the lack of monitoring. The patient might be non-complying in terms of taking medication, substance abuse or exercise without anybody knowing. IA agents can monitor the patient's activity and alert HP when non-compliance is detected.

Over-centralization is particularly problematic in long-term care.
Seniors are often pressured to move to institutions such as
assisted living so that they are closer to a medical staff. This, in
spite of significant medical, mental and financial cost of such a
move. An approach to long term care called ``aging in
place'' is gaining popularity around the world. IA sidekicks can help
seniors perform tasks without taking away their agency.


\subsection{IA and knowledge dissemination}

Through machine learning, IA sidekicks can adapt, over time, to the
medic using them. This is particularly true for pattern doctors
performing analysis of complex signals. Initially, the sidekick will
use some standard set of parameters which gives reasonable performance on
typical signals. Over time, the sidekick will learn to imitate the
doctor that is using it. At this point the sidekick captured some of
the recognition abilities of the doctor. The machine learning term for
the captured information is the ``learned model''.

Learned models, especially those corresponding to experienced and
successful doctors, are likely to be useful for other doctors,
possibly at the beginning of their career. Models from many doctors,
in many institutions, can be collected in repositories. Such models
will have many uses, from initializing sidekicks for new doctors,
through the integration of many models into a single better model.

IA models complement other methods of medical method dissemination
such as protocols, books, lectures and journal articles. Such models might have the advantage of capturing pattern recognition methods
which are often hard to describe in words. Training a cancer detection model is likely to require less effort and be more effective than writing a journal article that explains the same. \cite{reid2000medical}.

These models are likely to agree with each other on the easy cases, but are likely to disagree on the harder cases. By comparing the outputs of models trained by multiple experts on can distinguish the easy cases, on which a confident prediction can be made, from the harder cases, on which the diagnosis is IDK, and the doctor needs to use additional tests to arrive at a reliable diagnosis.

\section{About the Authors}
\input{Authors}

\section{References}
% \bibliographystyle{alpha} 
\bibliography{medbib}

\end{document}

