\Medicine{Uncertainty due to signal quality}{Medical devices use a
variety of bio-sensors that measure record and analyze different
  biometric signals. These signals vary in velocity from low-velocity vital signs such as heart rate,
  oxygen saturation, temperature and blood pressure, through
  mid-velocity waveforms such as ECG, EEG, \st{respiratory signal and arterial blood
  pressure.} to high velocity imaging such as CT, X-ray, MRI and
  scanning microscopes. Low-velocity signals such as blood
  pressure or heart rate can be directly used in diagnosis. Mid- and 
  high-velocity signals have to be interpreted before they can be used
  in diagnosis. We use the acronym HS to refer to mid and high
  velocity signals that require interpretation.

Interpreting HS is a significant fraction of the work of most
doctors. In addition, There are medical specializations such as
Radiology and Pathology that are devoted interpreting HS. These
so-called ``Pattern Doctors'' are predicted to be the early adopters
of AI~\cite{topol2019deep} or IA.

HS provides critical detailed information about the patient's
health. However, the richness of the signal can make it susceptible to
nuisance variability from noise, limited resolution, operator error
etc. The number and of nuisance variables is very large. In the next
paragraph we give an example of one nuisance variable: the placement
of ECG leads on the patient's body.

\yoav{Maybe add a figure explaining how ECG sensors should be placed? {\color{blue}--I don't think this is a good idea. For physicians, this is common sense. For non-physicians, who cares. But if you really think it is critical, we can add it for sure.]}
Also, what is the correct term? Sensor? Lead? something else? {\color{blue} -- Lead is more often used. But sensor is also fine.} }

\st{In other cases such as artifact removal of EEG is
 still an active research problem}~\cite{islam2016methods}

  
For ECG signals to be correctly and consistently interpreted, it is
important that the leads be placed correctly on the patient's
body. Several standards for placement have been published, for example, the standard 12 leads ECG system
\cite{goldberger2017clinical}, the EASI system \cite{Dower1988}, or the Frank lead system \cite{frank1956accurate}. %and {\color{blue}international 10–20 EEG
%systems} \cite{Klem1999TheTE} 
\yoav{I would prefer to focus on one
signal, i.e. ECG. {\color{blue}-- agreed. I have removed EEG.} Can we point to competing standard for lead placement
for ECG? {\color{blue}--updated} }

\st{to recently smart clothing system for telemedicine}
\cite{nesenbergs2016architecture} \yoav{off topic {\color{blue}--okay}}

It is not always possible to achieve a consistent and precise sensor
placement for biomedical signal collection due to various reasons, for example, the torso variation caused by gender, age and living styles.
\yoav{can you list some common ones? I imagine body type, areas that
are being treated, variation because of training .. 
{\color{blue} -- updated}}

This uncertainty might be tolerable for some clinical applications;
for example, an imprecise ECG sensor placement might not impact the
identification of some types of arrhythmia from the ECG signal, like
atrial fibrillation. However, this uncertainty might cause troubles in
identifying other types of arrhythmia, for example, premature atrial contraction.


\st{for example, an imprecise placement of the deep brain stimulation
      lead inside subthalamic nucleus might downgrade the Parkinson
      disease treatment outcome.}

\yoav{I would prefer to stick with ECG {\color{blue} -- agreed}}

}
